### 2024-10-07 esop25/ipj.tex
checkpoint

Our main type safety result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then cheating
  is detectable in $\prog$.
\end{theorem}

>>>>

Our main type safety result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then $\prog$
  has integrity.
\end{theorem}
